% Copyright (c) 2024 Denis Faraci

\documentclass[7pt]{article}
\usepackage[margin=0.3in]{geometry}
\usepackage{fontspec}
\setmainfont{Times New Roman}
\usepackage[colorlinks=true, urlcolor=black]{hyperref}
\usepackage{titlesec}
\usepackage{enumitem}
\titlespacing*{\section}{0pt}{0.7em}{.5em}
\newcommand{\sectionline}{\vspace{-0.3em}\noindent\rule{\linewidth}{0.15pt}\vspace{0.08em}}
\newcommand{\project}[3]{%
    \noindent
    \begin{tabular*}{\textwidth}{@{\extracolsep{\fill}} l r}
    \textbf{#1} & \textit{#2} \\
    \end{tabular*}
    \vspace{0.04em}
    #3
    \vspace{0.08em}\par
}
\newcommand{\cvsection}[2]{%
    \vspace{-.6em}
    \section*{{\large\textbf{\MakeUppercase{#1}}}}
    \vspace{-0.5em}
    \sectionline
    \vspace{-0.15em}
    #2
}
\newcommand{\footerdescription}[1]{%
    \vspace{-0.25em}
    \begin{center}
    \scriptsize
    \setlength{\parskip}{0pt}
    \setlength{\parindent}{0pt}
    \textit{#1}
    \end{center}
    \vspace{-0.25em}
}

\begin{document}
    \pagestyle{empty}

% Header
    \begin{tabular*}{\textwidth}{@{\extracolsep{\fill}} l r}
        &
        \begin{minipage}{0.22\textwidth}
            \vspace{-1.2em}
            \raggedright
            {\LARGE\textbf{Denis Faraci}}\\[0.08em]
            {\normalsize\textbf{Gameplay Programmer}}\\[0.08em]
            {\footnotesize
            Italy, Milan\\
            +39 339 1172868\\
            voydergames@gmail.com\\
            \href{https://zvoyder.github.io}{zvoyder.github.io}\\
            }
        \end{minipage}
    \end{tabular*}

% Sections
    \cvsection{SUMMARY}{
        Gameplay Programmer experienced in \textbf{Unreal Engine} and \textbf{Unity}, focused on scalable systems and clean architecture,
        developing modular \textbf{frameworks} for  \textbf{published titles} while collaborating with teams, adapting to workflows and working independently with self-motivation and ambition.
    }

    \cvsection{SKILLS}{
        \begin{itemize}[noitemsep, topsep=0pt, parsep=0pt, partopsep=0pt, itemsep=0pt, leftmargin=*]
            \item \textbf{Unreal Engine 5} – 3+ years in gameplay programming specializing in gameplay systems using \textbf{Blueprints and C++}, creating fully \textbf{data-driven} systems,  experienced with the \textbf{Gameplay Ability System} and the Engine source code; Two games published on \textbf{Steam}, one near release.
            \item \textbf{Unity} – 5+ years indie experience creating core gameplay systems, including frameworks. Published a game on \textbf{Google Play}.
            \item \textbf{Netcode} – Implemented multiplayer systems using the \textbf{Replication System in Unreal Engine} and \textbf{Mirror for Unity}, with experience integrating \textbf{Steamworks} and \textbf{Google Play Services} APIs.
            \item \textbf{C / C++ / C\# / .NET} – Developed desktop and console applications with a focus on \textbf{OOP}, memory management and performance.
            \item \textbf{UI Programming} – Created a modular node-based dialogue system with the \textbf{Unity UI Toolkit}, implemented different UI systems for multiple Unreal Engine plugins using its \textbf{UMG} and \textbf{Slate}.
            \item \textbf{Version Control / Git / GitHub} – Collaborated on multiple repositories using the \textbf{Git-Flow} branching model, resolving difficult conflicts, helping and mentoring team members to understand the best practices of version control.
            \item \textbf{Project Management / Jira / HacknPlan} – Worked on various projects, managing tasks, sprints, backlogs, and milestones. Supported interdepartmental collaboration using \textbf{agile workflows} and effective communication with the game design department.
            \item \textbf{UML / TDD} – Used UML for documentation and TDD to ensure reliable, maintainable code.
            \item \textbf{Python} – Used in Unreal for \textbf{automation}, integrating databases into DataAssets and using it for editor utilities.
            \item \textbf{CI/CD Pipelines} – Familiar with \textbf{automated workflows} for building, testing and deploying projects.
            \item \textbf{HTML / PHP / MySQL / JQuery / Javascript} – Developed websites, including a personal portfolio.
            \item \textbf{Java / Assembly} – Developed applications and contributed to technical projects across paradigms.
            \item \textbf{Microsoft Office} – Documentation, production planning and reporting.
        \end{itemize}
    }

    \cvsection{WORKS}{
        \project{\href{https://eventhorizonschool.itch.io/the-negative-edge}{The Negative Edge} - \textit{Unreal Engine 5.5}}{Nov 2024 - Current}{
            Developed core gameplay systems, including RPG mechanics, inventory, UI and Weapon System in Blueprint and C++, collaborating with design and art teams;
            achieved 2k+ views, 300 downloads and early feedback;
            showcased at \textbf{Gamescom} and \textbf{DevGAMM}, upcoming on Steam and released on Itch.io.
        }
        \project{\href{https://store.steampowered.com/app/4075260/Weabot/}{Weabot} - \textit{Unreal Engine 5.3}}{Jan 2024 - Jul 2024}{
            Developed modular core systems such as inventory, achievements, save system, AI, UI, project architecture and quality-of-life features;
            released on Steam and Itch.io.
        }
        \project{\href{https://jacedxxm.itch.io/self}{Self} - \textit{Unreal Engine 5.4}}{Nov 2024 - Dec 2024}{
            Sole programmer, developed core systems including AI, 3C, UI, inventory and a custom Input Register System vital for the horror mechanics;
            achieved 400+ views, gained exposure through YouTube videos; presented at \textbf{IGDA}, upcoming on Steam and released on Itch.io.
        }
        \project{VUEDK Framework - \textit{Unreal Engine 5.5+}}{Jan 2024 - Current}{
            Developed modular plugins for gameplay, UI, AI and utility systems, refined through years across multiple projects,
            receiving lots of feedback from different game designers, improving reusability and ease of use; upcoming on \textbf{FAB}.
        }
        \project{VUDK Framework - \textit{Unity 2022.3.10f1+}}{Jan 2023 - Current}{
            Developed a modular framework for gameplay, UI, AI and utility systems, including character controllers, input, checkpoints, saving, crafting, weapons, dialogue, exploration and more.
        }
    }

    \cvsection{EDUCATION}{
        \project{Event Horizon School - \textit{Final Grade: 30/30}}{Oct 2022 - Oct 2025}{
            Completed the Game Programming course of over 1000 hours, focusing on Unity C\# and Unreal C++;
            recognized for top performance throughout the program examinations.
        }
        \project{I.T.I.S. "C. FACCHINETTI" - \textit{Final Grade: 94/100}}{(self-directed study included) Sep 2015 - Oct 2022}{
            Completed a high school program in computer science and software engineering, collaborating on team projects;
            awarded a post-graduation scholarship and featured in local media.
        }
    }

    \cvsection{LANGUAGES}{
        \textbf{Italian} – Native; \textbf{English} – B2 (Professional working proficiency)
    }

    \footerdescription{
        I authorize the processing of my personal data contained in my CV in accordance with Legislative Decree 196/2003 and the GDPR (EU Regulation 2016/679).
    }
\end{document}
